Unifying Gompertzian growth with the communicable disease spreading paradigm

### 2023-01-03 letterToEditor/letter.tex
finalize

\recipient{To}{Editor, \\
               Bulletin of Mathematical Biology,\\ 
               }
\date{\today}
\opening{\textbf{Initial submission of manuscript titled: ``Unifying the communicable disease spreading paradigm with Gompertzian growth''}}
\closing{Sincerely yours, \vspace{-1em}}

@@

If you do decide to review this paper you may find the enclosed list of possible referees helpful. Some of them are listed in the references of the manuscript. Due to the conclusions of our paper, I request that this paper receives more reviews than your average, and at least 3 reviews. Some reviewers will probably have their scientific ``beliefs'' challenged. I would ask them to discern between dogma and observation. Science is only at the mercy of the latter.

@@

% \item Nigel D. Goldenfeld 
% \item Evans, Steven N.
% \item Altshuler, Boris L.
% \end{enumerate}
\textbf{List of possible referees}
\begin{enumerate}

\item Vladimir N. Binhi, vnbin@mail.ru, Prokhorov General Physics Institute of the Russian Academy of Sciences, 38 Vavilov St., 119991 Moscow, Russia
Is familiar with the biological effects due geomagnetic disturbances and fields.
\item Andrei B. Rubin, rubin@biophysics.msu.ru, Faculty of Biology, Lomonosov Moscow State University, Leninskie Gory 1/12, 119234 Moscow, Russia
Is familiar with the biological effects due geomagnetic disturbances and fields.
\item Viacheslav V. Krylov, I.D. Papanin Institute for Biology of Inland Waters Russian Academy of Sciences, Borok, Russian Federation, krylovviacheslav@mail.ru
Is intimately familiar with geomagnetic disturbances' effect on biology.
\item Marcin Molski, mamolski@amu.edu.pl, Adam Mickiewicz University, physics, Gompertz and quantum systems. Has done work on connecting the gompertz model to quantum coherent systems.
\item Takuya Yamano, yamano@amy.hi-ho.ne.jp, Department of Physics, Ochanomizu University, 2-1-1 Otsuka, Bunkyo-ku, 112-8610, Tokyo, Japan
Is familiar with the gompertz model as it relates to statistical physics.
\item Shigui Ruan, ruan@math.miami.edu, Professor of Mathematics, University of Miami, 
An editor of Bulletin of Mathematical Biology
\item Francesco Piazza, Francesco.Piazza@cnrs-orleans.fr, Max Planck Institute for the Physics of Complex Systems, physics, SIR models.
Has written one of the central papers modeling covid disease propagation from the SIR perspective. We have based our methods on their paper.
\item Rober M May, robert.may@zoo.ox.ac.uk, Professor of Zoology, University of Oxford, 
\item Chris G. Antonopoulos, canton@essex.ac.uk, U. of Essex, physics, chaos and SIR models.
Has written on the SIR model and chaotic dynamics.

>>>>

\recipient{To}{Editor, \\
               Journal of Mathematical Biology,\\ 
               }
\date{\today}
\opening{\textbf{Initial submission of manuscript titled: ``Unifying the communicable disease spreading paradigm with Gompertzian growth''}}
\closing{Sincerely yours, \vspace{-1em}}

@@

If you do decide to review this paper you may find the enclosed list of possible referees helpful. Some of them are listed in the references of the manuscript. Due to the conclusions of our paper, I request that this paper receives more reviews than your average, and at least 3 reviews.

@@

% \item Nigel D. Goldenfeld 
% \item Evans, Steven N.
% \item Altshuler, Boris L.
% \end{enumerate}
\textbf{List of possible referees}
\begin{enumerate}
\item Tom Britton, Dean of Mathematics and Physics, Stockholm University, tom.britton@math.su.se
\item Mark Lewis, marklewis@uvic.ca, Department of Mathematics and Statistics, University of Victoria
\item Alexandru Hening, Department of Mathematics at Texas A and M University,  ahening@tamu.edu
\item K-Y. Lam, Mathematics,  the Ohio State University, Columbus, lam.184@osu.edu 
\item X. Zou, Western University, London, Ontario, xzou@uwo.ca
\item S. Petrovskii, Mathematical Sciences, University of Leicester, sp237@le.ac.uk
\item Pierre Magal, Institut de Mathématiques de Bordeaux, Université de Bordeaux, pierre.magal@u-bordeaux.fr 
\item Vladimir N. Binhi, vnbin@mail.ru, Prokhorov General Physics Institute of the Russian Academy of Sciences, 38 Vavilov St., 119991 Moscow, Russia
Is familiar with the biological effects due geomagnetic disturbances and fields.
\item Andrei B. Rubin, rubin@biophysics.msu.ru, Faculty of Biology, Lomonosov Moscow State University, Leninskie Gory 1/12, 119234 Moscow, Russia
Is familiar with the biological effects due geomagnetic disturbances and fields.
\item Viacheslav V. Krylov, I.D. Papanin Institute for Biology of Inland Waters Russian Academy of Sciences, Borok, Russian Federation, krylovviacheslav@mail.ru
Is intimately familiar with geomagnetic disturbances' effect on biology.
\item Marcin Molski, mamolski@amu.edu.pl, Adam Mickiewicz University, physics, Gompertz and quantum systems. Has done work on connecting the gompertz model to quantum coherent systems.
\item Francesco Piazza, Francesco.Piazza@cnrs-orleans.fr, Max Planck Institute for the Physics of Complex Systems, physics, SIR models.
Has written one of the central papers modeling covid disease propagation from the SIR perspective. We have based our methods on their paper.
\item Robert M May, robert.may@zoo.ox.ac.uk, Professor of Zoology, University of Oxford.
\end{enumerate}

Other possible reviewers:
\begin{enumerate}
\item Joel Miller
\item Mark Chaplain
\item Vishwesha Guttal
\item Natalia Komorova
\item Shigui Ruan
\item Simon Levin

\item Helen Wearing
\item James Watmough
\item Jane Heffernan
\item Jing-an Cui
\item Julien Arino
